---
title: "Exploring Wild Data"
author: "Paloma Cartwright"
date: "10/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```

## Exploring the Wild Data about Mack Creek Salamander & Cutthroat Trout

#### Reading in the dataset and updating the column names to lower_snake_case 

```{r}

mack_verts <- read_csv(here::here("data", "AS00601.csv"), skip = 1) %>% 
  clean_names()
```

#### Exploring the dataset 

```{r}
# Store the 5th value in the weight column 
mc_wt_5 <- mack_verts$weight[5]
mc_wt_5

# Store the 8th to 20th values in the length1 column 
mc_length_8_20 <- mack_verts$length1[8:20]
mc_length_8_20

# Store everything in sample date as a vector 
# Commented this out because it was 1000 lines of output
# mc_dates <- mack_verts$sampledate
# mc_dates
```

#### Making a Salamander Subset 

```{r}

mc_salamanders <- mack_verts %>% 
  filter(species == "DITE")

```

#### Make a Scatterplot 

Scatterplot of Pacific Giant Salamander Data
```{r}

ggplot(data = mc_salamanders, aes(x = length1, y = weight)) +
  geom_point(aes(color = length1)) +
  scale_color_gradient(low="black", high="blue") +
  labs(title = "Snout-vent Length versus Weight of Pacific Giant Salamanders",
       x = "Snout-vent Length (mm)", 
       y = "Weight (g)", 
       color = "Length")

ggsave(here::here("figs", "salamander_size.png"))

```

Source: Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165 (Accessed 2021-08-10).


#### Make a Cutthroat Subset 

```{r}

mc_trout <- mack_verts %>% 
  filter(species == "ONCL")

```

#### Make a Scatterplot 

Scatterplot of Cutthroat Trout Data 

```{r}

ggplot(data = mc_trout, aes(x = length1, y = weight)) +
  geom_point(aes(color = reach)) + 
  scale_color_manual(values=c("purple", "blue", "darkgreen")) +
  labs(title = "Length vs Weight of Cutthroat Trout", 
       x = "Length (mm)",
       y = "Weight (g)",
       color = "Length Gradient") +
  facet_wrap(~reach)
  

ggsave(here::here("figs", "cutthroat_size.png"))

```





